Analysis of Odd one out experiment

### 2020-06-01 reports/DRM_exp/analysis_DRM_exp1.Rmd
code cleanup

p
ggsave(file.path(plots_dir, "Fig_chp4_results_accuracy.svg"), p, width = 6, height = 6)

@@

```{r}
df %>% 
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) +
  stat_summary(fun.data = "mean_cl_boot") +
  ylim(0,1) + theme(aspect.ratio = 1)

df %>% 
  ggplot(aes(x = type, y = correct)) +
  stat_summary(fun.data = "mean_cl_boot") +
  ylim(0,1) + theme(aspect.ratio = 1) +
  facet_wrap(~subject_id)

## Reaction times

### First remove rt larger than 5~s

```{r}
df_rt <- df %>% filter(rt_key <= 5)

### Descriptive statistics

```{r}
df_rt %>%
  group_by(subject_id, type) %>% 
  summarize(rt = mean(rt_key)) %>% 
  group_by(type) %>% 
  summarize(m_rt = mean(rt),sd_rt = sd(rt)) %>% 
  knitr::kable(digits = 2)
```

### Test differences in RT between stimuli

```{r}
lmRT_full <- lmer(log(rt_key) ~ type + (1+type|subject_id), df_rt)
lmRT_null <- lmer(log(rt_key) ~ 1 + (1+type|subject_id), df_rt)

anova(lmRT_full,lmRT_null)

summary(multcomp::glht(lmRT_full, linfct=multcomp::mcp(type="Tukey")))

df_rt %>%
  group_by(subject_id, type) %>% 
  summarize(rt = mean(rt_key)) %>% 
  arrange(subject_id, type) %>% 
  filter(type != "target") %>% 
  lsr::cohensD(rt ~ type, data = ., method = "paired")
```

### Visualize

```{r}
p <- df %>% 
  filter(rt_key < 5) %>% 
  ggplot(aes(x = rt_key)) + 
  theme(aspect.ratio = 1) +
  geom_histogram(binwidth = 0.2) + 
  xlab("RT [s]") + 
  theme(text = element_text(size = 24))
p
ggsave(file.path(plots_dir, "Fig_chp4_results_rt_hist.eps"), p, width = 6, height = 6)

p <- df_rt %>% 
  group_by(subject_id, type) %>% 
  summarize(rt = mean(rt_key)) %>% 
  ggplot(aes(x = type, y = rt)) + 
  theme(aspect.ratio = 1) +
  ylab("RT [s]") +
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Type") +
  theme(text = element_text(size = 24))
p
ggsave(file.path(plots_dir, "Fig_chp4_results_rt.svg"), p, width = 6, height = 6)
```

## split the analysis for first half and second half.

```{r}
trial_ids <- df %>% 
  filter(subject_id == 1) %>% 
  pull(trial_id)

cutoff_trial <- trial_ids[round(length(trial_ids)/15/2)*15]

df_acc2 <- df %>% mutate(part = if_else(trial_id<=cutoff_trial, "part1", "part2"))

df_acc2 %>% 
  group_by(type,part) %>% 
  summarize(m = mean(correct), sd = sd(correct)) %>% 
  knitr::kable(digits = 2)

p <- df_acc2 %>% 
  group_by(subject_id, type, part) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct, col = part, group = part)) +
  stat_summary(fun.data = "mean_cl_boot") +
  stat_summary(fun.y = "mean", geom = "line") +
  ylim(0,1) + theme(aspect.ratio = 1) +
  scale_color_discrete("Halves", labels = c("First half", "Second half")) +
  ylab("Perc. correct") + xlab("Type")

p

ggsave(file.path(plots_dir, "Fig_chp4_results_perhalves.svg"), p, width = 6, height = 6)
```

### Running mean for accuracy and rt

```{r}
df_rollmean <- df_acc2 %>% group_by(type) %>% 
  arrange(trial_id) %>% 
  mutate(correct = zoo::rollmean(correct, 250, align = "right", fill = NA), rt = zoo::rollmean(rt_key,250,align = "right", fill = NA))

p <-  df_rollmean %>% 
  ggplot(aes(x = trial_id, y = correct, col = type)) +
  geom_path() + 
  ylim(0,1) + 
  ylab("Perc. correct") + xlab("Trial id") + 
  theme(aspect.ratio = 0.5)

p

ggsave(file.path(plots_dir, "Fig_chp4_results_runningmean.svg"), p, width = 6, height = 6)

p <-  df_rollmean %>% 
  ggplot(aes(x = trial_id, y = rt, col = type)) +
  geom_path() + 
  ylab("Reaction time [s]") + xlab("Trial id") + 
  theme(aspect.ratio = 0.5)

p

ggsave(file.path(plots_dir, "Fig_chp4_results_runningmean_rt.svg"), p, width = 6, height = 6)

### Tests

```{r}
df_acc2 %>% group_by(subject_id,type,part) %>% summarize(correct = mean(correct)) %>% filter(type == "target") %>% t.test(correct~part,., paired = T, var.equal = T) %>% apa::apa()
```

## Analysis for first half and second half with respect to payment

```{r analysis payments}
trial_ids <- df %>% 
  filter(subject_id == 1) %>% 
  pull(trial_id)

cutoff_trial <- trial_ids[round(length(trial_ids)/15/2)*15]

df_acc2 <- df %>% mutate(part = if_else(trial_id<=cutoff_trial, "part1", "part2"))

df_acc2 %>% 
  group_by(type,part,payment) %>% 
  summarize(m = mean(correct), sd = sd(correct)) %>% 
  knitr::kable(digits = 2)

df_acc2 %>% 
  group_by(subject_id, type, part, payment) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct, col = part, group = part)) +
  stat_summary(fun.data = "mean_cl_boot") +
  stat_summary(fun.y = "mean", geom = "line") +
  ylim(0,1) + theme(aspect.ratio = 1) +
  facet_grid(~payment)

df_acc2 %>% 
  group_by(subject_id, payment) %>% 
  summarize(correct = mean(correct)) %>% 
  t.test(correct ~ payment, .)
```

```{r payment lmer}

lm1_full <- glmer(correct~type*payment+(1+type|subject_id) + (1|category), df, family = binomial())

lm1_justpayment <- glmer(correct~payment+(1+type|subject_id) + (1|category), df, family = binomial())

lm1_justtype <- glmer(correct~type+(1+type|subject_id) + (1|category), df, family = binomial())

lm1_nointeraction <- glmer(correct~type+payment+(1+type|subject_id) + (1|category), df, family = binomial())

lm1_null <- glmer(correct~1+(1+type|subject_id) + (1|category), df, family = binomial())

anova(lm1_justtype,lm1_null)
av1 <- anova(lm1_justpayment,lm1_null)
av1
av1$Chisq

anova(lm1_justtype,lm1_nointeraction)
anova(lm1_full,lm1_nointeraction)

```{r payment part lmer}

lm2_full <- glmer(correct~type*payment*part+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_justpayment <- glmer(correct~payment+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_justtype <- glmer(correct~type+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_justpart <- glmer(correct~part+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_justpart <- glmer(correct~part+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_nointeraction <- glmer(correct~type+payment+part +(1+type|subject_id) + (1|category), df_acc2, family = binomial())

lm2_null <- glmer(correct~1+(1+type|subject_id) + (1|category), df_acc2, family = binomial())

anova(lm2_justtype, lm2_null)
av1 <- anova(lm2_justpayment, lm2_null)
av1
av1$Chisq

anova(lm2_justtype, lm2_nointeraction)
anova(lm2_full, lm2_nointeraction)

The differences regarding payment is not significant.

@@

# there were problem with transparency, I needed to save it as svg and save manually as eps

ggsave(file.path(plots_dir, "Fig_chp4_results_ROC_oldclose.svg"), p1, width = 6, height = 6)

ggsave(file.path(plots_dir, "Fig_chp4_results_ROC_oldfar.svg"), p2, width = 6, height = 6)

@@

df_dprime2_da %>% select(da_oldclose,da_oldfar) %>% arrange(da_oldfar)
t.test(df_dprime2_da$da_oldclose, df_dprime2_da$da_oldfar, paired = T) %>% apa::apa()
lsr::cohensD(df_dprime2_da$da_oldclose, df_dprime2_da$da_oldfar,method = "paired")
```

@@

p_SDT_model <- df_plot %>% ggplot(aes(x = x, y = y, col = type)) + geom_path(size = 1.2) + geom_vline(xintercept = 0) +
  theme(aspect.ratio = 1)
p_SDT_model
ggsave(file.path(plots_dir, "Fig_chp4_results_dprimedistance.svg"), p_SDT_model, width = 6, height = 6)

@@

# Per image accuracy

```{r per image accuracy}
df_perimage <- df %>% group_by(img_name,type) %>% summarize(m = mean(correct), sd = sd(correct)) %>% arrange(-m)

order_category <- 
  df %>%
  group_by(category) %>% 
  do(Hmisc::smean.cl.boot(.$correct) %>% t() %>% as_tibble()) %>% 
  arrange(Mean) %>% 
  ungroup() %>% 
  mutate(category = forcats::as_factor(category), rank = 1:n())

p_ordercat <- order_category %>%
  ggplot(aes(x = category, xend = category, y = Lower, yend = Upper, group = 1)) +
  geom_segment(size = 1.2) +
  geom_point(aes(y=Mean), size = 3) + 
  theme(aspect.ratio = 0.2) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 16)) + 
  theme(legend.position = "top") + 
  xlab("Category") + 
  ylab("Accuracy")

p_ordercat
ggsave(file.path(plots_dir, "Fig_chp4_results_categories.svg"), p_ordercat, width = 9, height = 6)
```

# Memorability

Memorability were computed using pretrained CNN

```{r load mem data}
mem_imgnames <- read_csv(here("data/exp_DRM1/memorability/memorability_imgnames.txt"), col_names = F)
mem_values <- read_csv(here("data/exp_DRM1/memorability/memorability_all.txt"), col_names = F)

df_mem <- tibble(img_name = mem_imgnames$X1, mem_score = mem_values$X1)
dfm <- df_perimage %>% left_join(df_mem,by = "img_name") %>% rename(correct = m)

(cor.test(~correct+mem_score, dfm %>% filter(type == "target")) %>% papaja::apa_print.htest())$full_result
(cor.test(~correct+mem_score, dfm %>% filter(type == "close distractor")) %>% papaja::apa_print.htest())$full_result
(cor.test(~correct+mem_score, dfm %>% filter(type == "far distractor")) %>% papaja::apa_print.htest())$full_result
```

@@

## Correlation of distance from prototype with accuracy

```{r Correlation of distance from prototype with accuracy }

cor.test(~dist_to_proto+correct, df2)
cor.test(~dist_to_proto+correct, df2 %>% filter(type == "far distractor"))
cor.test(~dist_to_proto+correct, df2 %>% filter(type == "close distractor"))
cor.test(~dist_to_proto+correct, df2 %>% filter(type == "target"))

>>>>

p
ggsave(file.path(plots_dir, "Figure8.svg"), p, width = 6, height = 6)

@@

@@

ggsave(file.path(plots_dir, "Figure9_left.svg"), p1, width = 6, height = 6)

ggsave(file.path(plots_dir, "Figure_right.svg"), p2, width = 6, height = 6)

@@

df_dprime2_da %>% select(da_oldclose,da_oldfar) %>% arrange(da_oldfar)
t.test(df_dprime2_da$da_oldclose, df_dprime2_da$da_oldfar, paired = T) %>% apa::apa()
lsr::cohensD(df_dprime2_da$da_oldclose, df_dprime2_da$da_oldfar,method = "paired") %>% round(2)
```

@@

p_SDT_model <- df_plot %>% ggplot(aes(x = x, y = y, col = type)) + geom_path(size = 1.2) + geom_vline(xintercept = 0) +
  theme(aspect.ratio = 1)
p_SDT_model
ggsave(file.path(plots_dir, "Figure10.svg"), p_SDT_model, width = 6, height = 6)

@@

@@

### 2020-06-01 reports/odd_one_out/analysis_oddoneout.Rmd
code cleanup

metrics <- readRDS(file = here("data", "oddoneout", "metrics_200317.rds"))
metrics_wide <- readRDS(file = here("data", "oddoneout", "metrics_wide_200317.rds"))
wrong_trials <- df %>% select(prot_id_version,trial_id,im1:im9) %>% group_by(prot_id_version,trial_id) %>% gather("key", "value",im1:im9) %>% summarize(n = length(unique(value))) %>% filter(n<9) %>% select(-n)

@@

# Correlation of metrics

```{r}
df_metrics %>% select(ssim, hog, gist, sift_sum,pdistRGB) %>%  cor()
```

@@

p <- p0 + geom_point(data=predframe,colour="red")+
  geom_line(data=predframe,colour="red",aes(group=1)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  xlab("Distance ratio") + s
ylab("Perc. correct") +
  theme(text = element_text(size = 24))

>>>>

metrics <- readRDS(file = here("data", "oddoneout", "metrics_200317.rds"))

wrong_trials <- df %>% select(prot_id_version,trial_id,im1:im9) %>% group_by(prot_id_version,trial_id) %>% gather("key", "value",im1:im9) %>% summarize(n = length(unique(value))) %>% filter(n<9) %>% select(-n)

@@

@@

p <- p0 + geom_point(data=predframe,colour="red")+
  geom_line(data=predframe,colour="red",aes(group=1)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  xlab("Distance ratio") +
ylab("Perc. correct") +
  theme(text = element_text(size = 24))
